Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-03 mu/article/article.tex
Mu included in theory. Theory sec reorganized.

\section{Theory} % (fold)
\label{sec:theory}
The equation for $\mathcal{V}^{\mathrm{ab}}$ for normal incidence in the $xy$
plane with a polarization angle $\alpha$ is given by

\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

@@

@@

\subsection{Fixing spin}\label{sec:theory-fixspin}
In a similar way we can fix in the $xy$ plane the spin direction along the $x$,
$y$, and $z$ directions and then define the magnitude of the spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle $\gamma_{b}$
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}| (\omega)
&=
\sqrt{
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2}\ +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2}\ 
}, 
\label{eq:vs-mag}
\\
\gamma_{\mathrm{b}} (\omega)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ axis.

@@

\subsection{Fixing velocity.}\label{sec:theory-fixvel}
Considering that we have 2D structures we fixed the velocity in the $xy$ plane
along $x$ and $y$ directions and we define $|\mathcal{V}^{\mathrm{a}}|$ as
\begin{equation}
|\mathcal{V}^{\mathrm{a}}| (\omega)= 
\sqrt {
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{az}}(\omega))^{2} 
},
\label{eq:vv-mag}
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  (\omega)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega)}
{|\mathcal{V}^{\mathrm{a}}(\omega)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi (\omega)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

@@

>>>>

\section{Theory} % (fold)
\label{sec:theory}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Pure spin current %%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Pure spin-current} % (fold)
\label{sec:theory-pure_spin_current}

The spin density injection current $\dot{K}^{\mathrm{ab}}$ with speed along
direction $\mathrm{a}$ and spin polarization along $\mathrm{b}$ is defined as
\begin{equation}
\dot{K} = \mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
\label{eq:dotk}
\end{equation}
where
\begin{widetext}
\begin{equation}
\mu^{\mathrm{abcd}} (\omega) =
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}K}{8 \pi^{3}} \sum_{vcc'}^{'}
\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} ( 
r^{\mathrm{c}}_{vc'} 
r^{\mathrm{d}}_{cv } +
r^{\mathrm{d}}_{vc'} 
r^{\mathrm{c}}_{cv } ) \right]
\delta(\omega-\omega_{cv})
\label{eq:mu}
\end{equation}
\end{widetext}
is the corresponding spin density injection current pseudotensor. The $'$
in the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
covers these states.

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
which the spin polarized in the $\mathrm{b}$   direction moves along the
$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
polarization angle $\alpha$. Then,
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

@@

% section theory-pure_spin_current (end)

@@

\subsection{Fixing spin}\label{sec:theory-fixspin}
Considering that we have 2D structures we can fix the spin direction along the
$x$, $y$, and $z$ Cartesian coordinates and then define the magnitude of the
spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle
$\gamma_{b}$ as
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}| (\omega)
&=
\sqrt{
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2}\ +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2}\ 
}, 
\label{eq:vs-mag}
\\
\gamma_{\mathrm{b}} (\omega)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ axis.

@@

\subsection{Fixing velocity.}\label{sec:theory-fixvel}

In a similar way we can fix the velocity in the $xy$ plane
along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}|$ as
\begin{equation}
|\mathcal{V}^{\mathrm{a}}| (\omega)= 
\sqrt {
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{az}}(\omega))^{2} 
},
\label{eq:vv-mag}
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  (\omega)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega)}
{|\mathcal{V}^{\mathrm{a}}(\omega)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi (\omega)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
